Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-04-02 lqg-strings.tex

where the covariant derivative $\mc{D}_a$ is of the form:
\begin{equation}\label{eqn:covariant-deriv}
	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming

@@

\begin{equation}
	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
\end{equation}
where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$. We should therefore think of the embedding fields as $d+1$ dimensional vectors living in the fundamental representation of $\mathrm{SO}(d,1)$.

@@

>>>>

where the covariant derivative $\mc{D}_a$ is of the form:
\begin{equation}\label{eqn:covariant-deriv-v1}
	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming

@@

\begin{equation}\label{eqn:covariant-deriv-v2}
	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
\end{equation}
where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$. We should therefore think of the embedding fields as $d+1$ dimensional vectors living in the fundamental representation of $\mathrm{SO}(d,1)$.

@@

\textbf{From Embedding Fields:}

We take the bulk metric $g_{\mu\nu}$ to be flat. Let $\{\tau,\sigma\} := \{x^0, x^1\}$ be the spacetime co-ordinates on the worldsheet. Derivatives of the $X$'s in terms of these co-ordinates can be written as:
\begin{equation}
	\dot X := \left\{\frac{\partial X^\mu}{\partial \tau}\right\}; \quad X' := \left\{\frac{\partial X^\mu}{\partial \sigma}\right\}
\end{equation}
 we obtain the following form for the determinant of the worldsheet metric (\eqref{eqn:patch-area-v1}) in terms of the embedding fields:
\begin{align}\label{eqn:area-embedding}
	\det h & = \begin{vmatrix}
		h_{00} && h_{01} \\
		h_{10} && h_{11} 
	\end{vmatrix} = \begin{vmatrix}
		\dot X^2 && \dot X \cdot X' \\
		\dot X \cdot X' && X'^2
	\end{vmatrix} \nonumber \\
	& = \dot X^2 X'^2 - (\dot X \cdot X')^2
\end{align}

\textbf{From Vielbein:}

We can proceed to obtain the area of a 2-surface from the bulk vielbein as follows. Starting with the bulk vielbein $e_\mu^I$, we perform a local Lorentz transformation such that two ``legs'' of the vielbein are tangent to the worldsheet surface. We then project down the vielbein $e_\mu^I$ to a dyad $e_a^i$ living in the tangent space of the worldsheet, in terms of which the worldsheet metric can be written as:
\begin{equation}
	h_{ab} = e_a^i e_b^j \eta_{ij},
\end{equation}
where $\eta_{ij}$ is the flat $(1+1)$ Minkowski metric. The determinant then becomes:
\begin{align}\label{eqn:area-vielbein}
	\det h & = \begin{vmatrix}
		h_{00} && h_{01} \\
		h_{10} && h_{11} 
	\end{vmatrix} = \begin{vmatrix}
		e_x{}^i e_x{}^j & e_x{}^i e_y{}^j \\
		e_y{}^i e_x{}^j & e_y{}^i e_y{}^j
	\end{vmatrix} \eta_{ij} \nonumber \\
	& = \vec e_x{}^2 \vec e_y{}^2 - (\vec e_x \cdot \vec e_y)^2,
\end{align}
where $\vec e_x \cdot \vec e_y = e_x{}^i e_y{}^j \eta_{ij}$. It is clear by comparing the two expressions \eqref{eqn:area-embedding} and \eqref{eqn:area-vielbein} that we have the following correspondence between the vielbein the $X$ derivatives:
\begin{equation}
	\vec e_\tau \equiv \frac{\partial \vec X}{\partial \tau}; \quad \vec e_\sigma \equiv \frac{\partial \vec X}{\partial \sigma}.
\end{equation}
In other words we can identify the vielbein with the derivatives of the embedding fields. Of course, this is not altogether surprising. If we consider any manifold on which we have some set of fields $\{X^I(x^\mu)\}$, where $I$ is valued in the Lie algebra ${\mc g}$ of some group $\mc G$, as a function of some  ``fiducial'' co-ordinates $\{x^\mu\}$, then we can always define a set of ${\mc g}$ valued vector fields: 
$$
	e^I_\mu := \frac{\partial X^I}{\partial x^\mu}.
$$
In the usual formulation of the string action the embedding fields are \emph{not} Lie-algebra valued but are co-ordinate fields on what is generally taken to be a flat background. In order for this correspondence between vielbein and $X$ derivatives to work we have to view the $X$ fields as taking values in a Lie algebra. But these same $X$ fields \emph{also} serve as local co-ordinates for the bulk. In order for the co-ordinates to change from point to point in the bulk geometry, we must therefore have that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely! If $\mc A$ vanishes then that will imply that the fields $X$ don't change from one point to the next. Thus the amplitude $|\mc A|$ can be arbitrarily small but it can never be zero.
